Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection.~\cite{INHS}
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

Our work stands apart from previous work in that we are
addressing a different need. Lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.
NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories. Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results. Our goals and objectives are presented in the following section.

>>>>

Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

Our work stands apart from previous work in that we are
addressing a different need. Lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.

<--NOTE-NOTE-NOTE DAVE/JOEL/ALL - RE: above paragraph, I'm thinking we should we shift message a little bit to something like, e.g., "The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories. Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results. Our goals and objectives are presented in the following section.
